### 2015-05-07 papers/histogram/thesis/thesis.tex
fixed N=25 nw data and added u, hs, and s figures to thesis
some tweaks to figures

\begin{figure}[tb]
  \centering
  \includegraphics[width=0.47\textwidth]{figs/square-well.pdf}
  \caption[The square-well pair potential]{The square-well pair
    potential can be used to model short range forces to first
    order. The infinite potential at $r<\sigma$ simply enforces the
    condition that spheres cannot overlap. At $r>\lambda\sigma$, the
    potential is null, and makes no contribution to the fluid's
    internal energy.}
  \label{fig:pair_potential}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figs/dos-example.pdf}
  \caption[Density of states]{Sample density of states for square-well
    fluid with a well width $\lambda=1.3$, filling fraction
    $\eta=0.3$, and $N=25$ spheres, as computed by several histogram
    methods. The density of states has been normalized to have a
    maximum value of $1$.}
  \label{fig:dos_sample}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figs/transitions-example.pdf}
  \caption[Transition matrix]{Sample transition matrix $T_d\p{E,\Delta
      E}$ for square-well fluid with a well width $\lambda=1.3$,
    filling fraction $\eta=0.3$, and $N=25$ spheres.  The band at
    $\Delta E=0$ indicates that any given state is most likely to
    transition into another state with the same energy.}
  \label{fig:transitions_sample}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{figs/array-example.pdf}
  \caption[Example arrays]{Example arrays computed by various
    histogram methods for a square-well fluid with a well width
    $\lambda=1.3$, filling fraction $\eta=0.3$, and $N=25$ spheres
    after simulating for $10^5N^2$ iterations: (top left) energy
    histogram, (top right) weight array, (bottom left) density of
    states.}
  \label{fig:arrays}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/sample-rate-example.pdf}
  \caption[Example energy sampling rates]{Example pessimistic energy
    sampling rates computed by various histogram methods for a
    square-well fluid with a well width $\lambda=1.3$, filling
    fraction $\eta=0.3$, and $N=25$ spheres after simulating for
    $10^5N^2$ iterations.}
  \label{fig:sample_rates}
\end{figure}

\subsection{Errors in $u$, $c_V$, and $s_{\t{config}}$}
\label{sec:errors}

@@

\begin{figure}[H]
  \centering
  \caption[Internal energy]{Specific internal energy}
  \label{fig:u_error}
\end{figure}

\begin{figure}[H]
  \centering
  \caption[Heat capacity]{Specific heat capacity}
  \label{fig:cv_error}
\end{figure}

\begin{figure}[H]
  \centering
  \caption[Configurational entropy]{Specific configurational
    entropy}
  \label{fig:s_error}
\end{figure}

>>>>

\begin{figure}[tb]
  \centering
  \includegraphics[width=0.47\textwidth]{figs/square-well.pdf}
  \caption[The square-well pair potential]
  {The square-well pair potential can be used to model short range
    forces to first order. The infinite potential at $r<\sigma$ simply
    enforces the condition that spheres cannot overlap. At
    $r>\lambda\sigma$, the potential is null, and makes no
    contribution to the fluid's internal energy.}
  \label{fig:pair_potential}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figs/dos-example.pdf}
  \caption[Density of states]
  {Sample density of states for square-well fluid with a well width
    $\lambda=1.3$, filling fraction $\eta=0.3$, and $N=25$ spheres, as
    computed by several histogram methods. The density of states has
    been normalized to have a maximum value of $1$.}
  \label{fig:dos_sample}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figs/transitions-example.pdf}
  \caption[Transition matrix]
  {Sample transition matrix $T_d\p{E,\Delta E}$ for square-well fluid
    with a well width $\lambda=1.3$, filling fraction $\eta=0.3$, and
    $N=25$ spheres.  The band at $\Delta E=0$ indicates that any given
    state is most likely to transition into another state with the
    same energy.}
  \label{fig:transitions_sample}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{figs/array-example.pdf}
  \caption[Example arrays]
  {Example arrays computed by various histogram methods for a
    square-well fluid with a well width $\lambda=1.3$, filling
    fraction $\eta=0.3$, and $N=25$ spheres after simulating for
    $10^5N^2$ iterations: (top left) energy histogram, (top right)
    weight array, (bottom left) density of states.}
  \label{fig:arrays}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\textwidth]{figs/sample-rate-example.pdf}
  \caption[Example energy sampling rates]
  {Example pessimistic energy sampling rates computed by various
    histogram methods for a square-well fluid with a well width
    $\lambda=1.3$, filling fraction $\eta=0.3$, and $N=25$ spheres
    after simulating for $10^5N^2$ iterations.}
  \label{fig:sample_rates}
\end{figure}

\subsection{Thermodynamic properties and errors: $u$, $c_V$, and
  $s_{\t{config}}$}
\label{sec:errors}

@@

\begin{figure}[H]
  \centering
    \includegraphics[width=0.7\textwidth]{figs/internal-energy.pdf}
  \caption[Internal energy]
  {Specific internal energy}
  \label{fig:internal_energy}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/heat-capacity.pdf}
  \caption[Heat capacity]
  {Specific heat capacity}
  \label{fig:heat_capacity}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\textwidth]{figs/config-entropy.pdf}
  \caption[Configurational entropy]
  {Specific configurational entropy}
  \label{fig:config_entropy}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\textwidth]
  {figs/internal-energy-err.pdf}
  \caption[Errors in internal energy]
  {Errors in specific internal energy}
  \label{fig:internal_energy_err}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\textwidth]{figs/heat-capacity-err.pdf}
  \caption[Errors in heat capacity]
  {Errors in specific heat capacity}
  \label{fig:heat_capacity_err}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\textwidth]{figs/config-entropy-err.pdf}
  \caption[Errors in configurational entropy]
  {Errors in specific configurational entropy}
  \label{fig:config_entropy_err}
\end{figure}
